---
title: "monkeytronics.reports2 vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{monkeytronics.reports2 vignette}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# monkeytronics.reports2

<!-- badges: start -->
<!-- badges: end -->

The goal of `{monkeytronics.reports}` is to package and containerize the code for producing
flexdashboards for Monkeytronics.

## Installation

You can install the development version of monkeytronics.reports like so:

```{r, eval = FALSE}
# forthcoming, not sure about the full repo tree
# meanwhile, clone the repo and `Install and Restart`
# or `devtools::load_all()`
remotes::install_bitbucket(repo = "monkeytronics/r-analytics", subdir = "monkeytronics.reports")
```

## Example

```{r}
library(monkeytronics.reports2)
```

The code has been converted to functions. The `setup` part is in the package DESCRIPTION file. 
This along with `roxygen` creates the namespace with all imports/exports.

For ease of testing, I've wrapped some test params in a function:

```{r}
test_params()
```

The `wrangle` chunk now can be run as follows:

```{r}
# wrangled_devices <- wrangle_devices(test_params()$filtered_devices)
# wrangled_weather <- wrangle_weather(
#  filtered_weather = test_params()$filtered_weather,
#  from_timestamp = test_params()$fromTimeStamp,
#  to_timestamp = test_params()$toTimeStamp
# )
# wrangled_obs <- wrangle_observations(
#  filtered_obs = test_params()$filtered_obs,
#  from_timestamp = test_params()$fromTimeStamp,
#  to_timestamp = test_params()$toTimeStamp,
#  devices = wrangled_devices,
#  weather = wrangled_weather
#)
# data_volume <- get_data_volume(
#  observations = wrangled_obs,
#  from_timestamp = test_params()$fromTimeStamp,
#  to_timestamp = test_params()$toTimeStamp
#  )
# wrangled_devices <- remove_excluded_devices(
#  target_data = wrangled_devices,
#  data_volume = data_volume
# )
# wrangled_obs <- remove_excluded_devices(
#  target_data = wrangled_obs,
#  data_volume = data_volume
# )
```

Next, we can set some options for available data and colors:

```{r}
# monkey_palettes(devices = wrangled_devices)
# set_options(observations = wrangled_obs)
```

Finally, we should have everything to make a time series plot for humidity:

```{r}
# ts_chart(
#   observations = wrangled_obs,
#  from_timestamp = test_params()$fromTimeStamp,
#  to_timestamp = test_params()$toTimeStamp,
#  target_variable = "hum"
# )
```

And temperature:

```{r}
# ts_chart(
#  observations = wrangled_obs,
#  from_timestamp = test_params()$fromTimeStamp,
#  to_timestamp = test_params()$toTimeStamp,
#  target_variable = "temp"
# )
```

# Creating the flexdash report

We have a function `?knit_home_report` that takes 
    - a list of parameters (paths to data and timestamps)  
    - output file name (so we can keep track of requests if needed)
    - output directory (we need this to tell the docker container where on the host to drop the files)

We run this like so:

```{r, eval = FALSE}
# the system.file calls are to access the example data installed with the package
# in production, the list of parameters will be generated by the script calling this
# report

obs  <- system.file("data/filtered_obs.csv", package = "monkeytronics.reports")
dev  <- system.file("data/filtered_devices.csv", package = "monkeytronics.reports")
wea  <- system.file("data/filtered_weather.csv", package = "monkeytronics.reports")
int  <- system.file("data/filtered_interventions.csv", package = "monkeytronics.reports")
from <- 1627639151
to   <- 1630317551

par_list <- make_params_list(
  filtered_obs = obs,
  filtered_devices = dev,
  filtered_weather = wea,
  filtered_interventions = int,
  fromTimeStamp = from,
  toTimeStamp = to
)

# knit with default file name and output dir
# knit_home_report(par_list)
```

# Creating the report from docker

The package comes with an `R` script that calls `knit_home_report` (`run-home-report.R`)
and a bash wrapper that calls this `R` script (`home.sh`). These are copied inside the
docker container on build. `home.sh` becomes the `ENTRYPOINT` which is the script run
every time we start the container. `home.sh` and `run-home-report.R` take two command line
arguments: the file name and output dir. 

```{bash, eval = FALSE}
# home.sh my_report.html my_reports_folder
```

In a docker setting `my_reports_folder` should be a host folder mounted on the container. 
This makes sure the html output will be available outside the container after the latter 
has finished the job.

```{bash, eval = FALSE}
# docker build -t mtr .
# mkdir reports_folder
# docker run -v /full/path/to/reports/folder:/home/reports_folder mtr report.html /home/report_folder
```


